\documentclass[margin,line]{resume}
%\documentclass[margin,line,a4paper]{resume}
\usepackage{times}

\usepackage[usenames]{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tabularx}
\itemsep=0in
\parsep=0in
\textwidth=6.0in
\oddsidemargin -.5in
\evensidemargin -.5in
\topmargin -0.5in
\textheight=11in

\sloppy

\newenvironment{list1}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\renewcommand{\baselinestretch}{1.05}

% a new tabularx column type with centering
\newcolumntype{C}{>{\centering\arraybackslash}X}

%\pagestyle{fancy}
%\fancyhf{} %delete the current section for header and footer
%\fancyfoot[CE,CO]{\thepage\ of \pageref{LastPage}}
%\renewcommand{\headrulewidth}{0.0pt}

\name{Dr Tristan Friedrich KLEINSCHMIDT}

\begin{document}

\begin{resume}

%\color[rgb]{0.15,0.15,0.15}
%\pagecolor[rgb]{0.6,0.9,0.9}
\section{\sc Nationality}
Australian

\section{\sc Date of Birth}
30th of December 1983

\section{\sc Contact Information}

\parbox[t]{3.3in}{%
Unit 5, 13 Toms Court\\
Bayswater, WA 6053\\
Australia
}
\parbox[t]{2.3in}{%
{\it Phone}: +61 4 3978 6345  \\
%{\it Fax}: +61 7 3138 1827  \\
{\it Email}: {kleinschmidt\_tf@yahoo.com.au}
}

%\section{\sc Objective}
%To be actively involved in the research and development of speech- and speaker-based technologies, in particular their practical applications across a wide range of engineering operations. Longer-term plans are to advance into an academic position with responsibility for continuing the advanced research efforts of an institution in this field

%\section{\sc Research Interests}
%Speech recognition, speech enhancement, speech dialogue systems, in-car speech systems

\section{\sc Education}
{\bf Doctor of Philosophy (Elec Eng)} \hfill {\it January 2006 -- March 2010}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
\begin{list2}
\item Dissertation Title: {\it ``Robust Speech Recognition using Speech Enhancement''}
\item Principal Supervisor:  Professor Sridha Sridharan
\item Associate Supervisor: Dr Michael Mason
\item Key Research Areas: Automotive Speech Recognition and Speech Enhancement
\end{list2}
\end{list1}

{\bf Graduate Certificate in Research Commercialisation} \hfill {\it March 2008 -- June 2008}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.5 of 7.0
%\end{list2}
\end{list1}

{\bf Master of Engineering Science (Computer \& Communications)} \hfill {\it February 2005 -- January 2006}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.75 of 7.0
%\end{list2}
\end{list1}

{\bf Bachelor of Engineering (Electrical \& Computer) with First Class Honours} \hfill {\it February 2002 -- July 2005} \\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.9 of 7.0
%\end{list2}
\end{list1}

\section{\sc Professional Experience}
{\textbf{Simulation Consultant} (Full Time)} \hfill {\it January 2012 -- Current}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it TSG Consulting, Perth, WA}
\item The responsibilities of this position include:
\begin{list2}
\item Ongoing validation of holistic mining supply chain simulation models for large mining client.
\item Investigation of product mix in future mining operations and capacity planning.
\end{list2}
\end{list1}

{\textbf{Research Associate} (Full Time)} \hfill {\it January 2010 -- January 2012}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Airports of the Future Project, Queensland University of Technology}
\item The responsibilities of this position include:
\begin{list2}
\item Simulation of passenger flows within airport passenger buildings for determining level of service.
\item Supervision of PhD students and provision of operational guidance to other research staff.
\item Active interaction, negotiation and liaison with all project industry partners, external investigators, and research facilities at both industry sites and the partnered universities.
\item Ongoing project management including monitoring, evaluation of research milestones and project deliverables, as well as research and infrastructure support for the research team.
\item Preparation of progress and project reports to industry partners, the Industry Advisory Committee and the Australian Research Council.
\item Preparation of applications for national competitive funding sources including the Australian Research Council, National Security Science Technology Branch, and the Queensland Government.
\item Public website administration and access control for internal project web services.
\item Oral presentations for industry stakeholders to outline current project progress and advertise the project to the wider aviation community.
\end{list2}
\end{list1}

{\bf Sessional Academic} \hfill {\it March 2003 -- November 2011}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Faculty of Built Environment \& Engineering, Queensland
    University of Technology}
\item Main subject material taught:
\begin{list2}
\item Software system design from problem analysis through to software development and testing.
\item Programming in Matlab, C/C++.\\
\end{list2}
\item Responsibilities undertaken during these positions:
\begin{list2}
\item Development and delivery of lecture and tutorial material.
\item Facilitation and grading of verbal and written examination.
\item Continual evaluation of student feedback on all aspects of teaching; I have maintained a mean teaching rating of 4.35 out of 5 as evaluated by students.
\end{list2}
\end{list1}

\newpage

{\textbf{PhD Candidate} (Full Time)} \hfill {\it January 2006 -- March 2010}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Speech and Audio Research Laboratory, Queensland University of Technology}
\item The research conducted during this candidature
    focussed on single-channel speech enhancement techniques specifically for automatic speech recognition
    applications. Particular areas of work included:
%
%\newpage\opening{\hspace{-0.17in}Tristan Friedrich KLEINSCHMIDT}
%
\begin{list2}
\item Analysis and development of the use of phase spectrum
    information for spectral subtractive speech enhancement for automatic speech
    recognition.
\item Implementation of likelihood-maximising frameworks for
    speech enhancement within speech dialogue systems for in-car speech recognition.
\item Management of the collection and validation of an in-car
    speech database recorded by native Australian speakers in Australian
    driving conditions.
\item All development work was conducted on a Linux cluster using
    a mixture of C++, Matlab, Perl, and Unix scripts.
\item Attended professional development workshops and courses on topics such as research skills, public policy, research commercialisation, leadership and entrepreneurship.
\end{list2}
\end{list1}

{\textbf{Research Assistant} (as required)} \hfill {\it January 2006 -- December 2009}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Speech and Audio Research Laboratory, Queensland University of Technology}
\item This work was conducted as part of a joint project between
    General Motors Holden, LaTrobe University and QUT as part of
    the Co-operative Research Centre for Advanced Automotive
    Technology~(AutoCRC). The responsibilities and particular work
    undertaken were:
\begin{list2}
\item Demonstration to key stakeholders of proof-of-concept in-car speech system for
    navigation systems.
\item Integration of spectral subtraction and delay-and-sum
    beamforming for in-car speech recognition.
\item Validation testing of FPGA designs for
    single-channel spectral subtraction and dual-channel delay-and-sum
    beamforming.
\item Development of spectral subtraction for simplified,
    low-resource implementation on an FPGA.
\item Microphone and microphone location testing for for
    multi-channel in-car speech data collection.
\item Compilation of work from full three year project into final
    project report.
\item Preparation and submission of funding applications.
\end{list2}
\end{list1}

{\bf Visiting Research Scholar} \hfill {\it April 2009 -- July 2009}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Center for Robust Speech Systems, University of Texas at Dallas, TX, USA}
\item This invited internship position was primarily for the
    assessment of speech dialogue systems for in-car speech
    applications. The work undertaken involved:
\begin{list2}
\item Analysis of driver cognitive load when using in-car speech dialogue systems, including analysis of speech response delay against variables such as familiarity with English, and CAN-bus signals.
\item Development of in-car speech data collection capturing changing noise conditions \emph{during} driver's speech.
\item Development of speech dialogue systems for in-car simulation data collection aimed at capturing various aspects of driver cognitive load during dialogue system interaction.
\end{list2}
\end{list1}

%\newpage \opening{Tristan Kleinschmidt}

\section{\sc Honours and Awards}
{ Australian Postgraduate Award Scholarship, 2006--2009.\\
\setlength{\parskip}{1ex}
Vice-Chancellors Postgraduate Scholarship, 2006--2009. \\
AutoCRC Postgraduate Scholarship, 2006--2009. \\
QUT University Medal, 2006. \\
ASSTA PhD Study Award, 2006. \\
Induction to Golden Key International Honour Society, 2003.\\
Dean's List of Students with Excellent Academic Record, 2002,
2003, 2004, 2005. }

\section{\sc Current Memberships}
{
 IEEE, Full Member since 2009.\\
% International Speech Communication Association (ISCA), since 2006.\\
 Australian Speech Science \& Technology Association (ASSTA), since 2006. \\
 Golden Key International Honour Society, since 2003.
}

\section{\sc Other Experience}
{ Membership Coordinator -- Built Environment \&
Engineering Dean's Scholars Alumni Group, 2006--2010. \\
Delegate to Robotics \& Autonomous Systems Student Forum, 2005.}

\section{\sc Computer Skills}
\begin{list2}
\item Languages: C/C++, Perl, UNIX scripting, Java, VBA, Siman.
\item Applications: \LaTeX, Matlab, ARENA, HTK, Microsoft Visual Studio, Office suite including
    Powerpoint, Excel and Access.
\item Operating Systems: Windows and UNIX/Linux.
\end{list2}
\newpage
%\section{\sc Referees}
%{
%\parbox[t]{3.0in}{%
%{\bf Professor Sridha Sridharan} \\
%Professor \\
%School of Engineering Systems \\
%Queensland University of Technology\\
%{\it Phone}: +61 7 3138 2113    \\
%{\it Email}: s.sridharan@qut.edu.au
%}
%\setlength{\parskip}{1.5ex}
%\parbox[t]{3.0in}{%
%Prof.~Sridharan is the leader of the Speech and Audio Research Laboratory and deputy director of the Information Security Institute at QUT. He has over 18 years of experience in speech research with more than 250 publications.
%{\bf Professor John HL Hansen} \\
%Professor and Department Head \\
%Department of Electrical Engineering \\
%University of Texas at Dallas, USA\\
%{\it Phone}: +1 972 883 2910    \\
%{\it Email}: john.hansen@utdallas.edu
%}
%
%%\vspace*{-1.0mm}
%\parbox[t]{2.45in}{%
%{\bf Professor John HL Hansen} \\
%Professor and Department Head \\
%Department of Electrical Engineering \\
%University of Texas at Dallas, USA }
%\parbox[t]{3.5in}{%
%}

%\parbox[t]{3.0in}{%
%{\bf Dr Michael Mason} \\
%Senior Staff Engineer, Audio Advanced Development \\
%Dolby Australia \\
%{\it Phone}: +61 2 9101 79992     \\
%{\it Email}: Michael.Mason@dolby.com
%}
%\parbox[t]{3.5in}{%

%}


%}


%\newpage
%\namefont{List of Publications}
  %\opening{List of Publications }
  \opening{Tristan Friedrich KLEINSCHMIDT}
%#\vskip 2pt
%\fullline

\section{\sc Publications}
{
%{\bf Journal Articles:}
%%\setlength{\parskip}{0ex}
%%
%\begin{enumerate}
%   \setlength{\itemsep}{1pt}
%   \setlength{\parsep}{0pt}
%   \setlength{\parskip}{0pt}
%
%\item {\bf R.~Vogt} and S.~Sridharan, ``Explicit modelling of session variability for speaker verification,'' {\em Computer Speech \& Language}, vol.~22, no.~1, pp.~17--38, 2008.
%\end{enumerate}
%%
%\vspace{1ex}
%%
%{\bf Patents:}
%%
%\begin{enumerate}
%   \setlength{\itemsep}{1pt}
%   \setlength{\parsep}{0pt}
%   \setlength{\parskip}{0pt}
%
%\item {\bf R.~Vogt}, M.~Mason, and S.~Sridharan, \emph{Confidence measures for speaker verification}, PCT/AU2006907080, 2006.
%%\setlength{\parskip}{2ex}
%
%\item J.~Pelecanos, S.~Sridharan, and {\bf R.~Vogt}, \emph{Model adaptation system and method for speaker recognition}, PCT/AU2004001718, 2004.
%\end{enumerate}
%
%\vspace{1ex}
%
{\bf Book Chapters:}
\begin{enumerate}
\item{\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason, "``A Likelihood-Maximizing Framework for Enhanced In-Car Speech Recognition Based on Speech Dialog System Interaction,'' in \emph{Digital Signal Processing for In-Vehicle Systems and Safety}, Springer Science+Business Media, LLC, 2012, pp.~159-174.
\end{enumerate}

{\bf Journal Articles:}
\begin{enumerate}
	  \setlength{\itemsep}{2pt}
	  \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}

\item {\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason, ``The Use of Phase in Complex Spectrum Subtraction for Robust Speech Recognition,'' \emph{Computer Speech \& Language}, vol.~25, 2011, pp.~585-600.
\end{enumerate}


{\bf Conference Articles:}
%
\begin{enumerate}
    \setlength{\itemsep}{2pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}

\item A.~Harrison, V.~Popovic, B.~Kraal, {\bf T.~Kleinschmidt}, ``Challenges in Passenger Terminal Design: A Conceptual Model of Passenger Experience,'' to be presented at the \emph{Design Research Society Conference}, 2012.

\item S.~Shuchi, R.~Drogemuller, {\bf T.~Kleinschmidt}, ``Flexible Airport Terminal Design: Towards a Framework'', to be presented at the \emph{IIE Asian Conference}, 2012.

\item {\bf T.~Kleinschmidt}, X.~Guo, W.~Ma, P.K.D.V.~Yarlagadda, ``Including Airport Duty-Free Shopping in Arriving Passenger Simulation and the Opportunities this Presents,'' presented at the \emph{Winter Simulation Conference}, (Phoenix, AZ, USA), December 2011.

\item W.~Ma, {\bf T.~Kleinschmidt}, C.~Fookes, P.K.D.V.~Yarlagadda, ``Check-in Processing: Simulation of Passengers with Advanced Traits,'' presented at the \emph{Winter Simulation Conference}, (Phoenix, AZ, USA), December 2011.

\item R.~Navarathna, {\bf T.~Kleinschmidt}, D.~Dean, S.~Sridharan, P.~Lucey, ``Can Audio-Visual Speech Recognition outperform Acoustically Enhanced Speech Recognition in Automotive Environment?'' to be presented at \emph{INTERSPEECH}, (Florence, Italy), August 2011.

\item H.~Bo$\mathrm{\check{r}}$il, O.~Sadjadi, {\bf T.~Kleinschmidt} and J.~H.~L.~Hansen, ``Analysis and Detection of Cognitive Load and Frustration in Drivers' Speech,'' in \emph{Proceedings of INTERSPEECH}, (Makuhari, Japan), pp.~502-505, 2010.

\item {\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason, ``The Application of Phonetic Distribution Normalisation to Likelihood-Maximising Speech Enhancement for Robust ASR,'' in \emph{Proceedings of the Speech Schience \& Technology Conference}, (Melbourne, Australia), pp.~118-121, 2010.

\item {\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason, ``The Effect of Dialect Mismatch on Likelihood-Maximising Speech Enhancement for Noise-Robust Speech Recognition,'' in \emph{Proceedings of the Speech Schience \& Technology Conference}, (Melbourne, Australia), pp.~114-117, 2010.

\item J.~Whittington, H.~Ye, K.~Kamalakannan, N.V.~Vu, M.~Mason, {\bf T.~Kleinschmidt}, and S.~Sridharan, ``Low-Cost Hardware Speech Enhancement for Improved Speech Recognition in Automotive Environments'', in \emph{Proceedings of the 24th Australian Road Research Board Conference}, (Melbourne, Australia), pp.~1-17, 2010.

\item {\bf T.~Kleinschmidt}, M.~Mason, E.~Wong and
    S.~Sridharan, ``The Australian English speech corpus for
    in-car speech processing,'' in \emph{Proceedings of the
    34th IEEE International Conference on Acoustics, Speech and
    Signal Processing}, (Taipei, Taiwan), pp.~4177-4180, 2009.

\item {\bf T.~Kleinschmidt}, P.~Boyraz, H.~Bo$\mathrm{\check{r}}$il, S.~Sridharan and
    J.~H.~L.~Hansen, ``Assessment of Speech Dialog Systems using Multi-Modal Cognitive Load Analysis and Driving Performance Metrics,'' in \emph{Proceedings of the 5th IEEE International Conference on Vehicle Electronics and Safety}, (Pune, India), pp.~167-172, 2009.

\item H.~Ye, J.~Whittington, I.~Himawan, {\bf T.~Kleinschmidt}
    and M.~Mason, ``FPGA implementation of dual-microphone
    delay-and-sum beamforming for in-car speech enhancement
    and recognition,'' in {\em Proceedings of the AutoCRC
    Conference}, (Melbourne, Australia), 2009.

\item J.~Whittington, K.~Deo, {\bf T.~Kleinschmidt} and
    M.~Mason, ``FPGA implementation of spectral subtraction
    for in-car speech enhancement and recognition,'' in {\em
    Proceedings of the 2nd International Conference on Signal
    Processing and Communication Systems}, (Gold Coast,
    Australia), 2008.

\item {\bf T.~Kleinschmidt}, D.~Dean, S.~Sridharan and
    M.~Mason, ``A continuous speech recognition protocol for
    the AVICAR database,'' in \emph{Proceedings of the 1st
    International Conference on Signal Processing and
    Communication Systems}, (Gold Coast, Australia),
    pp.~339-344, 2007.

\item {\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason, ``A
    modified LIMA framework for spectral subtraction applied
    to in-car speech recognition,'' in \emph{Proceedings of
    the 1st International Conference on Signal Processing and
    Communication Systems}, (Gold Coast, Australia),
    pp.~335-338, 2007.
\end{enumerate}
}

\newpage
{\bf Invited Keynote Papers:}
\begin{enumerate}
\item {\bf T.~Kleinschmidt}, A.~Goonetilleke, C.~Fookes, and P.K.D.V.~Yarlagadda, ``A Multi-Disciplinary Approach for the Design and Management of Airport Terminals'', in \emph{Proceedings of the All India Machine Tool Design and Research Conference}, (Andhra Pradesh, India), pp.~57-62, 2010.
\end{enumerate}

{\bf Workshop Papers:}
%
\begin{enumerate}
    \setlength{\itemsep}{2pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}

\item J.~Whittington, K.~Deo, {\bf T.~Kleinschmidt} and
    M.~Mason, ``FPGA implementation of spectral subtraction
    for automotive speech recognition,'' in {\em IEEE Workshop
    on Computational Intelligence in Vehicles and Vehicular
    Systems}, (Nashville, TN, USA), pp.~72-79, 2009.

\item {\bf T.~Kleinschmidt}, S.~Sridharan and M.~Mason,
    ``Likelihood-maximising frameworks for enhanced in-car
    speech recognition,'' in \emph{4th Biennial Workshop on
    DSP for In-Vehicle Systems and Safety}, (Dallas, TX, USA),
    2009.

\end{enumerate}

\vspace{4ex}
\section{\sc Conference Presentations}
\begin{list2}
\item Winter Simulation Conference, Phoenix, AZ, USA, December 2011 (2 papers).
\item HCSNet SummerFest, Sydney, Australia, December 2009.
\item 4th Biennial Workshop on DSP for In-Vehicle Systems
    and Safety, Dallas, TX, USA, June 2009.
\item 34th IEEE International Conference on Acoustics, Speech, and
    Signal Processing, Taipei, Taiwan, April 2009 (2 papers).
\item 1st International Conference on Signal Processing and
    Communication Systems, Gold Coast, Australia, December 2007 (2 papers).
\end{list2}
%
%\section{\sc Patents}
%{

%\newpage
%\namefont{List of Publications}
  %\opening{List of Publications }
  %\opening{Robert Jeffrey VOGT}
%#\vskip 2pt
%\fullline

\end{resume}

\end{document}
