\documentclass[margin,line]{resume}
%\documentclass[margin,line,a4paper]{resume}
\usepackage{times}

\usepackage[usenames]{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tabularx}
\itemsep=0in
\parsep=0in
\textwidth=6.0in
\oddsidemargin -.5in
\evensidemargin -.5in
\topmargin -0.5in
\textheight=11in

\sloppy

\newenvironment{list1}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\renewcommand{\baselinestretch}{1.05}

% a new tabularx column type with centering
\newcolumntype{C}{>{\centering\arraybackslash}X}

%\pagestyle{fancy}
%\fancyhf{} %delete the current section for header and footer
%\fancyfoot[CE,CO]{\thepage\ of \pageref{LastPage}}
%\renewcommand{\headrulewidth}{0.0pt}

\name{Tristan Friedrich KLEINSCHMIDT}

\begin{document}

\begin{resume}

%\color[rgb]{0.15,0.15,0.15}
%\pagecolor[rgb]{0.6,0.9,0.9}
\section{\sc Nationality}
Australian

\section{\sc Date of Birth}
30th of December 1983

\section{\sc Contact Information}

\parbox[t]{3.3in}{%
Unit 19, 44 Brisbane Street\\
Toowong, QLD 4066\\
Australia
}
\parbox[t]{2.3in}{%
{\it Phone}: +61 7 3138 4769  \\
{\it Mob}: +61 4 3978 6345  \\
{\it Email}: kleinschmidt\_tf@yahoo.com.au}

%\section{\sc Objective}
%To be actively involved in the research and development of speech- and speaker-based technologies, in particular their practical applications across a wide range of engineering operations. Longer-term plans are to advance into an academic position with responsibility for continuing the advanced research efforts of an institution in this field

%\section{\sc Research Interests}
%Speech recognition, speech enhancement, speech dialogue systems, in-car speech systems

\section{\sc Education}
{\bf Doctor of Philosophy (Elec Eng)} \hfill {\it January 2006 -- March 2010}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
\begin{list2}
\item Dissertation Title: {\it ``Robust Speech Recognition using Speech Enhancement''}
\item Supervisors: Professor Sridha Sridharan, Dr Michael Mason
\item Key Research Areas: Automotive Speech Recognition and Speech Enhancement
\end{list2}
\end{list1}

{\bf Graduate Certificate in Research Commercialisation} \hfill {\it March 2008 -- June 2008}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.5 of 7.0
%\end{list2}
\end{list1}

{\bf Master of Engineering Science (Computer \& Communications)} \hfill {\it February 2005 -- January 2006}\\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.75 of 7.0
%\end{list2}
\end{list1}

{\bf Bachelor of Engineering (Electrical \& Computer) with First Class Honours} \hfill {\it February 2002 -- July 2005} \\\vspace{-0.85\baselineskip}
\begin{list1}
\item[] Queensland University of Technology, Brisbane, Australia
%\begin{list2}
%\item GPA: 6.9 of 7.0
%\end{list2}
\end{list1}

\section{\sc Professional Experience}
{\textbf{Project Officer} (Full Time)} \hfill {\it January 2010 -- Current}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Airports of the Future Project, Queensland University of Technology}
\item The responsibilities and skills gained in this position include:
\begin{list2}
\item Simulation of passenger flows within airport terminals using agent-based methodologies, including the expansion of models to include activities outside of the necessary formalities for boarding an aircraft.
\item Conceptual development of agent-based simulation frameworks in order to address a wide range of complex scenarios in airport terminals.
\item Modelling (and in particular simplification) of the complex nature of airport operations, providing a strong overview into the challenges of succeeding in this environment.
\item Development and analysis of airport process models describing passenger facilitation across all stakeholders in order to make recommendations to improve efficiency, security and passenger experience.
\item Analysis of the activities passengers actually undertake within the airport environment including airport retail.
\item Development of models capable of describing, monitoring and evaluating airport performance with respect to passenger facilitation.
\item Reasoning behind use of physical spaces required for current and future services within the airport, and how this might affect passenger facilitation efficiency and the passenger experience.
\item Project management including monitoring and evaluation of project milestones and deliverables, as well as providing research and infrastructure support for a research team of 30 personnel.
\item Preparation of progress and project reports to aviation industry partners, and key governmental agencies including the Australian Research Council.
%\item Development of research proposals Preparation of applications for national competitive funding sources including the Australian Research Council, National Security Science Technology Branch, and the Queensland Government.
\item Active interaction, liaison and negotiation with all project partners from the aviation industry, external investigators, and research facilities at both industry sites and partnered universities to ensure the ongoing success of the project.
\item Regular presentations to industry stakeholders outlining project progress and outcomes and advertise the project to the wider aviation community.
\item Participation at industry workshops focussing on future aviation environments within Australia.
\item Provision of high-level technical research oversight to the research directions of the project to ensure alignment with industry expectations.
\item Supervision of PhD students and provision of operational guidance to other research staff.
%\item Public website administration and access control for internal project web services.
%\item Development of health \& safety risk management plans.
\end{list2}
\end{list1}
\newpage
\section{\sc Other Experience}
{\bf Sessional Academic} \hfill {\it March 2003 -- May 2010}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Faculty of Built Environment \& Engineering, Queensland
    University of Technology}
%\item Subjects:
%\begin{list2}
%\item ENB246 Engineering Problem Solving (Lecturer/Tutor) -- 2007--2010.
%\item ENB241 Software Systems Design (Tutor) -- 2005--2009.
%\item EEB584 Introduction to Design (Lecturer/Tutor) -- 2005, 2006.
%\item CEB109 Engineering Mechanics 1 (Tutor) -- 2003.\\
%\end{list2}
\item Main subject material taught:
\begin{list2}
\item Engineering software system design from problem analysis through to software development and testing.
\item Programming in Matlab, C/C++.
\end{list2}
%\item Skills developed:
%\begin{list2}
%\item Development and delivery of lecture and tutorial material with a focus on clarity of understanding.
%\item Facilitation, grading and evaluation of verbal and written examination.
%\item Continual evaluation of student feedback on all aspects of teaching; I have maintained a mean teaching rating of 4.35 out of 5 as evaluated by students which is higher the the university and faculty averages.
%\end{list2}
\end{list1}

{\textbf{PhD Candidate} (Full Time)} \hfill {\it January 2006 -- March 2010}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Speech and Audio Research Laboratory, Queensland University of Technology}
\item Key responsibilities and skill attained: %The research conducted during this candidature
%    focussed on single-channel speech enhancement techniques specifically for automatic speech recognition
%    applications. Particular areas of work included:
%
%\newpage\opening{\hspace{-0.17in}Tristan Friedrich KLEINSCHMIDT}
%
\begin{list2}
\item In-depth review and detailed analysis of existing engineered systems through interpretation of technical documentation.
\item Identification and development of creative engineering solutions to identified challenges.
\item Effective time and project management skills to ensure on-time delivery of candidature milestones.
\item Collection and validation of data for evaluation of system performance.
\item Software system development and testing.
\item Attendance at professional development workshops and courses on topics on public policy, commercialisation, leadership and entrepreneurship.

\end{list2}
\end{list1}

{\textbf{Research Assistant} (as required)} \hfill {\it January 2006 -- December 2009}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Speech and Audio Research Laboratory, Queensland University of Technology}
\item This work was conducted as part of a joint project between
    General Motors Holden, LaTrobe University and QUT as part of
    the Co-operative Research Centre for Advanced Automotive
    Technology~(AutoCRC). The responsibilities and particular work
    undertaken were:
\begin{list2}
\item Demonstration to key stakeholders of proof-of-concept in-car speech system for
    navigation.
\item Participation in industry workshops on future challenges in the Australian automotive industry.
\item Proof-of-concept experimentation to validate the integration of previously independent sub-systems for improvement of overall system performance.
\item Adaptation of speech recognition system to enable low-cost solutions.% to increase chances of widespread industry adoption.
\item Compilation of work from full three year project into final project report.
\item Preparation and submission of applications for future industry-based projects.
\end{list2}
\end{list1}

{\bf Visiting Research Scholar} \hfill {\it April 2009 -- July 2009}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Center for Robust Speech Systems, University of Texas at Dallas, TX, USA}
%\item This invited internship position was primarily for the
    %assessment of speech dialogue systems for in-car speech
%    applications.
\item The work undertaken involved:
\begin{list2}
\item Statistical analysis of existing engineered systems in order to assess performance and to establish anomalies within the user group.
\item Development of data collection and validation protocols to measure effects of adverse conditions on user behaviour with the system.
\end{list2}
\end{list1}

{\bf Technical Assistant} (Part-Time \& Vacation) \hfill {\it November 2002 -- February 2005}\\
\vspace{-0.85\baselineskip}
\begin{list1}
\item {\it Wide Bay Water Corporation, Hervey Bay}
\item Skills developed / responsibilities:
\begin{list2}
\item Management of systems design.
\item Interpretation of technical documentation, and understanding how individual components affect the overall system.
\item Communication with residents of the local government area.
\item Prioritisation of tasks to ensure on-time delivery of milestones.
\end{list2}
\end{list1}

%{\bf Service Cashier} (Casual) \hfill {\it November 2002 -- February 2005}\\
%\vspace{-0.85\baselineskip}
%\begin{list1}
%\item {\it Woolworths Pty. Ltd., Hervey Bay \& Toowong}
%Skills developed / responsibilities:
%\begin{list2}
%\item Customer relations and extensive sales experience.
%\item Stock and shrinkage management.
%\item Team work.
%\end{list2}
%\end{list1}

%\newpage \opening{Tristan Kleinschmidt}

\section{\sc Honours and Awards}
{ Australian Postgraduate Award Scholarship, 2006--2009.\\
\setlength{\parskip}{1ex}
Vice-Chancellors Postgraduate Scholarship, 2006--2009. \\
AutoCRC Postgraduate Scholarship, 2006--2009. \\
QUT University Medal, 2006.}

%\section{\sc Current Memberships}
%{
% IEEE, Full Member since 2009.\\
% Golden Key International Honour Society, since 2003.
%}

\section{\sc Service}
{ Mentoring Coordinator -- Built Environment \&
Engineering Dean's Scholars Alumni Group, 2006--Current. }%\\
%Delegate to Robotics \& Autonomous Systems Student Forum, 2005.}

\section{\sc Computer Skills}
\begin{list2}
\item Applications: Office suite including
    Powerpoint, Excel and Access, productivity suites including Adobe Acrobat Pro and Adobe Contribute, Matlab. %\LaTeX, Matlab, %    HTK, Microsoft Visual Studio.
\item Operating Systems: Windows and UNIX/Linux.
\item Programming Languages: C/C++, Perl, UNIX scripting, Visual Basic.
\item Simulation environments: AnyLogic, Repast Simphony.
\end{list2}
\vspace{1.85\baselineskip}
\newpage
\section{\sc Referees}
{

%\parbox[t]{3.0in}{%
{\bf Professor Ashantha Goonetilleke} \\
Professor and Industry Liaison -- Airports of the Future \\
School of Urban Development \\
Faculty of Built Environment \& Engineering \\
Queensland University of Technology\\
{\it Phone}: +61 7 3138 1539    \\
{\it Email}: a.goonetilleke@qut.edu.au
%}

%\parbox[t]{3.0in}{%
{\bf Dr Michael Mason} \\
Lecturer \\
School of Engineering Systems\\
Queensland University of Technology\\
{\it Phone}: +61 4 1049 5708    \\
{\it Email}: m.mason@ieee.org
%}

%\parbox[t]{3.0in}{%
{\bf Mr Stephen Goodwin} \\
General Manager -- Operations \\
Brisbane Airport Corporation \\
{\it Phone}: +61 7 3406 3000    \\
{\it Email}: stephen.goodwin@bne.com.au
%}
%\setlength{\parskip}{1.5ex}

%\parbox[t]{3.0in}{%
{\bf Mr Matthew Cox} \\
Manager -- Passenger Analysis Unit \\
Australian Customs and Border Protection Service \\
{\it Phone}: +61 2 6275 6943 \\
{\it Email}: matthew.cox@customs.gov.au
%}

%}


}


\end{resume}

\end{document}
